Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-04-30 tex/ms.tex
subsections, revert to emulateapj

We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
\mu(\theta, \lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma_v) \otimes 
S(\lambda, t, Z [, \beta]) \, e^ {-k_\lambda\tau_V} 
\\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta \right]
\quad ,
\end{eqnarray} where the parameters $\theta$ include the stellar mass
$m_*$, effective optical depth to dust in the $V$-band $\tau_V$,
velocity dispersion $\sigma_v$, luminosity distance $d_L$, and
redshift $z$.  The spectrum of one solar mass of stars that formed at
time $t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$
where the additional parameters $\beta$ may include details of the
population synthesis model, such as the IMF slope and adjustments to
the stellar spectra or stellar evolutionary tracks
\citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
purposes of this exercise, with no loss of generality (KEEPING IMF
SLOPE CONSTANT FOR NOW).  We will also fix the shape of the
attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ to the Milky
way average of \citet{CCM89} and assume that $d_L$ is known to high
precision from independent methods. (BDJ NOTE TO SELF - do not use $k$
for the attenuation curve shape - will confuse people used to
reddening curves)

@@

We calculate $\mu$ using the Flexible Stellar Population Synthesis
code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
\citep{Padova} and high-resolution theoretical stellar spectra
\citep{CKC14} which allow us to probe super-solar metallicities at
early ages.  NEBULAR EMISSION - MASK OR INFER?

BDJ/DRW WORDS ABOUT DATA

We estimate the posterior through MCMC sampling. Our sampling of the
posterior is accomplished using \texttt{emcee} \cite{dfm} after an
intial round of optimization using Powell's method.  \texttt{emcee} is
an implementation of the affine-invariant ensemble sampler of
\citet{GW}, and unlike typical Metropolis-Hastings MCMC sampling does
not require the specification of step sizes in each dimension.  Our
prior distributions are in all cases top-hat functions, though more
informative priors distributions may be used.  Informative priors may
be especially appropriate for the calibration parameters $\alpha$ if
additional information about the instrument is available or for the
parameters of interest $\theta$, for example in the case where there
is knowledge of the metallicity distribution of the population from
which a given cluster is drawn.

>>>>

\subsection{Data}
BDJ/DRW WORDS ABOUT DATA

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
\mu(\theta, \lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma_v) \otimes 
S(\lambda, t, Z [, \beta]) \, e^ {-k_\lambda\tau_V} 
\\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta \right]
\quad ,
\end{eqnarray} where the parameters $\theta$ include the stellar mass
$m_*$, effective optical depth to dust in the $V$-band $\tau_V$,
velocity dispersion $\sigma_v$, luminosity distance $d_L$, and
redshift $z$.  The spectrum of one solar mass of stars that formed at
lookback time $t$ with metallicity $Z$ is given by $S(\lambda, t, Z [,
\beta])$ where the additional parameters $\beta$ may include details
of the population synthesis model, such as the IMF slope and
adjustments to the stellar spectra or stellar evolutionary tracks
\citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
purposes of this exercise, with no loss of generality (KEEPING IMF
SLOPE CONSTANT FOR NOW).  We will also fix the shape of the
attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ to the Milky
way average of \citet{CCM89} with $R_V=3.1$ and assume that $d_L$ is
known to high precision from independent methods. (BDJ NOTE TO SELF -
do not use $k$ for the attenuation curve shape - will confuse people
used to reddening curves.  Even though it's super handy.)

@@

We calculate $S(\lambda, t, Z)$ using the Flexible Stellar Population
Synthesis code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
\citep{Padova} and high-resolution theoretical stellar spectra
\citep{CKC14} which allow us to probe super-solar metallicities at
early ages.  NEBULAR EMISSION - MASK OR INFER?  The model spectra are
smoothed by convolution with a Gaussian in velocity space, and are
interpolated to the wavelength points of the of the observed spectrum
taking into account the redshift.

\subsection{Sampling and Priors}
We estimate the posterior through MCMC sampling. Our sampling of the
posterior is accomplished using \texttt{emcee} \cite{dfm} after an
intial round of optimization using Powell's method.  \texttt{emcee} is
an implementation of the affine-invariant ensemble sampler of
\citet{GW}, and unlike typical Metropolis-Hastings MCMC sampling does
not require the specification of step sizes in each dimension.  Our
prior distributions are in all cases top-hat functions, though more
informative priors distributions may be used.  Informative priors may
be especially appropriate for the calibration parameters $\alpha$ if
additional information about the instrument is available or for the
parameters of interest $\theta$, for example in the case where there
is knowledge of the metallicity distribution of the population from
which a given cluster is drawn.
